---
title: "Benchmark lengte en gewicht - iHD"
date: "2023-12-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Voorbereiding

```{r, message=FALSE, warning=FALSE}

require(tidyverse)
require(RODBC)
```


## Noemer ophalen uit IQVIA DWH

```{r, message=FALSE, warning=FALSE}

### optie 1: via file
#### Ophalen noemer
noemer <-  read_csv2(noemer.csv")


### optie 2: via query:
sql_query <- "SELECT
                v_ha_deflt_hapat_curr_patient.deflt_hapat_bk AS patiënt___business_sleutel, 
                v_ha_hcend_time_time.hcend_time_year_rnk AS ontslagdatum___jaar, 
                v_ha_deflt_haadmfile_administrative_file.deflt_haadmfile_bk AS administratief_dossier___business_sleutel, 
                v_ha_deflt_haclnfile_clinical_file.deflt_haclnfile_bk AS medisch_dossier___business_sleutel, 
                SUM(v_f_ha_care_episode_dyn.hacarepsd_main_gate_admission_qty) AS zorgperiode___aantal_grote_poort_opnames, 
                v_ha_last_inpat_habedidx_bedindex.last_inpat_habedidx_bk AS C___bedindex__administratief____business_sleutel
            FROM
                dbo.v_ha_deflt_haadmfile_administrative_file v_ha_deflt_haadmfile_administrative_file
                    INNER JOIN dbo.v_f_ha_care_episode_dyn v_f_ha_care_episode_dyn
                    ON v_ha_deflt_haadmfile_administrative_file.deflt_haadmfile_key = v_f_ha_care_episode_dyn.deflt_haadmfile_key
                        INNER JOIN dbo.v_ha_deflt_haclnfile_clinical_file v_ha_deflt_haclnfile_clinical_file
                        ON v_ha_deflt_haclnfile_clinical_file.deflt_haclnfile_key = v_f_ha_care_episode_dyn.deflt_haclnfile_key
                            INNER JOIN dbo.v_ha_deflt_hapat_curr_patient v_ha_deflt_hapat_curr_patient
                            ON v_ha_deflt_hapat_curr_patient.deflt_hapat_key = v_f_ha_care_episode_dyn.deflt_hapat_key
                                INNER JOIN dbo.v_ha_hcend_time_time v_ha_hcend_time_time
                                ON v_ha_hcend_time_time.hcend_time_key = v_f_ha_care_episode_dyn.hcend_time_key
                                    INNER JOIN dbo.v_ha_last_inpat_habedidx_bedindex v_ha_last_inpat_habedidx_bedindex
                                    ON v_ha_last_inpat_habedidx_bedindex.last_inpat_habedidx_key = v_f_ha_care_episode_dyn.last_inpat_habedidx_key 
            WHERE 
                v_ha_hcend_time_time.hcend_time_year_rnk IN (2021,
                    2022 ) AND
                v_ha_last_inpat_habedidx_bedindex.last_inpat_habedidx_bk IN ( 
                    'C', 
                    'E', 
                    'G' ) AND
                v_f_ha_care_episode_dyn.hacarepsd_main_gate_admission_qty > 0 
            GROUP BY 
                v_ha_deflt_hapat_curr_patient.deflt_hapat_bk, 
                v_ha_hcend_time_time.hcend_time_year_rnk, 
                v_ha_deflt_haadmfile_administrative_file.deflt_haadmfile_bk, 
                v_ha_deflt_haclnfile_clinical_file.deflt_haclnfile_bk, 
                v_ha_last_inpat_habedidx_bedindex.last_inpat_habedidx_bk"



```


## Lengte en gewicht ophalen uit je EPD

```{r, message=FALSE, warning=FALSE}

### connectie met postgress maken voor lengte en gewicht voor alle adremanummmers
pg_conn <- create_postgres_connection()

weight_final <- noemer %>%
  left_join(weight_selection) 

## code specifiek UZG weggelaten!

height_final <- noemer %>%
  left_join(height_selection) 
```


# Start benchmark

## Prepare the data

This are all the codes containing information on how to perform the assessment.
You need to do this for the 3 seperate cases: Pediatrics, Geriatrics, Surgery. 

## 1. Create a dataset for patients' weight

This is an example dataset. In this step you should read in your file containing Weight.
Please make sure that you use the same terms for the dataset: `weight_data`.

This will provide you with 3 datasets: 

- `weight_data_geriatry`, 
- `weight_data_surgical`, 
- `weight_data_pediatry`

This serves as an example.

- `weight_data_geriatry <- data.frame(Patient_ID = 1:20, Weight_kg = c(70, 65, 80, 72, 75, 68, 90, 82, 78, 69, 71, 74, 79, 73, 76, 85, 77, 88, 81, 84) )`
- repeat for surgical: `weight_data_surgical`
- repeat for pediatry: `weight_data_pediatry`



```{r}
#library(ggplot2)
#library(dplyr)

# This are all the codes containing information on how to perform the assessment.
# You need to do this for the 3 seperate cases: Pediatrics, Geriatrics, Surgery. 

# 1. Create a dataset for patients' weight
## This is an example dataset. In this step you should read in your file containing Weight.
## Please make sure that you use the same terms for the dataset --> weight_data.
## This will provide you with 3 datasets: weight_data_geriatry, weight_data_surgical, weight_data_pediatry
### This serves as an example.
# weight_data_geriatry <- data.frame(
#   Patient_ID = 1:20,
#   Weight_kg = c(70, 65, 80, 72, 75, 68, 90, 82, 78, 69, 71, 74, 79, 73, 76, 85, 77, 88, 81, 84)
# )
### repeat for surgical: weight_data_surgical
### repeat for pediatry: weight_data_pediatry

weight_data <- weight_final %>%
  rename(Weight_kg = gewicht_kg,
         Patient_ID = medisch_dossier___business_sleutel,
         bedindex = C___bedindex__administratief____business_sleutel) %>%
  select(bedindex, Patient_ID, Weight_kg)

weight_data_geriatry <- weight_data %>% filter(bedindex == "G")
weight_data_surgical <- weight_data %>% filter(bedindex == "C")
weight_data_pediatry <- weight_data %>% filter(bedindex == "E")

```

## 2. Create a dataset for patients' length

This is an example dataset. In this step you should read in your file containing Length.
Please make sure that you use the same terms for the dataset: `length_data`.

This will provide you with 3 datasets: 

- `length_data_geriatry`, 
- `length_data_surgical`, 
- `length_data_pediatry`
 
This serves as an example: 

- `height_data_geriatry <- data.frame( Patient_ID = 1:20, Height_m = c(1.65, 1.70, 1.75, 1.60, 1.72, 1.68, 1.80, 1.78, 1.73, 1.66, 1.71, 1.64, 1.69, 1.67, 1.82, 1.74, 1.83, 1.76, 1.81, 1.79) )`
- repeat for surgical: `height_data_surgical`
- repeartfor pediatry: `height_data_pediatry`


```{r }



height_data <- height_final %>%
  mutate(Height_m = lengte_cm / 100) %>%
  rename( Patient_ID = medisch_dossier___business_sleutel,
          bedindex = C___bedindex__administratief____business_sleutel) %>%
  select(bedindex, Patient_ID, Height_m)

height_data_geriatry <- height_data %>% filter(bedindex == "G")
height_data_surgical <- height_data %>% filter(bedindex == "C")
height_data_pediatry <- height_data %>% filter(bedindex == "E")
```

## 3. Completeness

**Calculate the percentage of missing values for length_data**

```{r}

completeness_score_height_geriatry <- (1 - mean(is.na(height_data_geriatry$Height_m))) * 100
completeness_score_height_surgical <- (1 - mean(is.na(height_data_surgical$Height_m))) * 100
completeness_score_height_pediatry <- (1 - mean(is.na(height_data_pediatry$Height_m))) * 100
```


**Calculate the percentage of missing values for weight_data**

```{r}
completeness_score_weight_geriatry <- (1 - mean(is.na(weight_data_geriatry$Weight_kg))) * 100
completeness_score_weight_surgical <- (1 - mean(is.na(weight_data_surgical$Weight_kg))) * 100
completeness_score_weight_pediatry <- (1 - mean(is.na(weight_data_pediatry$Weight_kg))) * 100
```



**Print the percentages of missing values**

### Resuls COMPLETENESS

**HEIGHT** 

* Completeness score for height_data_geriatry: `r round(completeness_score_height_geriatry,2)`
* Completeness score for height_data_surgical:  `r round(completeness_score_height_surgical,2)`
* Completeness score for height_data_pediatry: `r round(completeness_score_height_pediatry,2)` 

**WEIGHT**

* Completeness score for weight_data_geriatry: `r round(completeness_score_weight_geriatry,2)` 
* Completeness score for weight_data_surgical: `r round(completeness_score_weight_surgical,2)` 
* Completeness score for weight_data_pediatry: `r  round(completeness_score_weight_pediatry,2)` 


##  4. Consistency - WEIGHT - geriatry and surgical

**Filter out missing values**
```{r}
weight_data_filtered_geriatry <- weight_data_geriatry %>%
  filter(!is.na(Weight_kg))
weight_data_filtered_surgical <- weight_data_surgical %>%
  filter(!is.na(Weight_kg))
```

**Calculate the percentage of weight values within the specified range - GERIATRY**
```{r}
within_range_weight_geriatry <- weight_data_filtered_geriatry %>%
  filter(Weight_kg >= 40, Weight_kg <= 160)

percentage_within_range_weight_g <- (nrow(within_range_weight_geriatry) / nrow(weight_data_filtered_geriatry)) * 100
percentage_outside_range_weight_g <- 100 - percentage_within_range_weight_g


```



**Calculate the percentage of weight values within the specified range - SURGICAL**
```{r}
within_range_weight_surgical <- weight_data_filtered_surgical %>%
  filter(Weight_kg >= 40, Weight_kg <= 160)

percentage_within_range_weight_s <- (nrow(within_range_weight_surgical) / nrow(weight_data_filtered_surgical)) * 100
percentage_outside_range_weight_s <- 100 - percentage_within_range_weight_s


```





## 5. Consistency - WEIGHT - pediatry

**Filter out missing values**

```{r}
weight_data_filtered_pediatry <- weight_data_pediatry %>%
  filter(!is.na(Weight_kg))
```

**Calculate the percentage of weight values within the specified range - PEDIATRY**

```{r}
within_range_weight_pediatry <- weight_data_filtered_pediatry %>%
  filter(Weight_kg >= 1, Weight_kg <= 80)

percentage_within_range_weight_p <- (nrow(within_range_weight_pediatry) / nrow(weight_data_filtered_pediatry)) * 100
percentage_outside_range_weight_p <- 100 - percentage_within_range_weight_p

```



## 5. Consistency - HEIGHT - geriatry and surgical

**Filter out missing values**

```{r}
height_data_filtered_geriatry <- height_data_geriatry %>%
  filter(!is.na(Height_m))
height_data_filtered_surgical <- height_data_surgical %>%
  filter(!is.na(Height_m))
```


**Calculate the percentage of height values within the specified range - GERIATRY**

```{r}
within_range_height_geriatry <- height_data_filtered_geriatry %>%
  filter(Height_m >= 1.4, Height_m <= 2.2)

percentage_within_range_height_geriatry <- (nrow(within_range_height_geriatry) / nrow(height_data_filtered_geriatry)) * 100
percentage_outside_range_height_geriatry <- 100 - percentage_within_range_height_geriatry



```


**Calculate the percentage of height values within the specified range - SURGICAL**

```{r}
within_range_height_surgical <- height_data_filtered_surgical %>%
  filter(Height_m >= 1.4, Height_m <= 2.2)

percentage_within_range_height_surgical <- (nrow(within_range_height_surgical) / nrow(height_data_filtered_surgical)) * 100
percentage_outside_range_height_surgical <- 100 - percentage_within_range_height_surgical

```



## 6. Consistency - HEIGHT - pediatry

**Filter out missing values**

```{r}
height_data_filtered_pediatry <- height_data_pediatry %>%
  filter(!is.na(Height_m))
```

**Calculate the percentage of height values within the specified range - PEDIATRY**

```{r}
within_range_height_pediatry <- height_data_filtered_pediatry %>%
  filter(Height_m >= 0.40, Height_m <= 2)

percentage_within_range_height_pediatry <- (nrow(within_range_height_pediatry) / nrow(height_data_filtered_pediatry)) * 100
percentage_outside_range_height_pediatry <- 100 - percentage_within_range_height_pediatry


```

### Resuls CONSITENCY

**WEIGHT**

* Consistency score for weight GERIATRY - within range: `r round(percentage_within_range_weight_g,2)`
* Consistency score for weight GERIATRY - outside range: `r round(percentage_outside_range_weight_g,2)`
* Consistency score for weight SURGICAL - within range: `r round(percentage_within_range_weight_s,2)`
* Consistency score for weight SURGICAL - outside range: `r round(percentage_outside_range_weight_s,2)`
* Consistency score for weight PEDIATRY - within range: `r round(percentage_within_range_weight_p,2)`
* Consistency score for weight PEDIATRY - outside range: `r round(percentage_outside_range_weight_p,2)`


**HEIGHT** 

* Consistency score for height GERIATRY - within range: `r round(percentage_within_range_height_geriatry,2)`
* Consistency score for height GERIATRY - outside range: `r round(percentage_outside_range_height_geriatry,2)`
* Consistency score for height SURGICAL - within range: `r round(percentage_within_range_height_surgical,2)`
* Consistency score for height SURGICAL - outside range: `r round(percentage_outside_range_height_surgical,2)`
* Consistency score for height PEDIATRY - within range: `r round(percentage_within_range_height_pediatry,2)`
* Consistency score for height PEDIATRY - outside range: `r round(percentage_outside_range_height_pediatry,2)`

